---
title: "esm206_lab8"
author: "Jessica West"
date: "11/16/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
```

### Read in slo_homes.csv

```{r}
homes <- read_csv("slo_homes.csv")
```

### Create a subset with 4 cities

Task: create a subset (called homes_subset) that only contains observations where the city is:

- "San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

### A little exploration

Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sale status

```{r}
homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price),
            sd_sqft = sd(SqFt))
```

Task: explore the relationship between square footage and home price (from homes_subset) in a scatterplot

```{r}
ggplot(data = homes_subset, aes(x = SqFt, y = Price)) +
  geom_point() +
  geom_smooth(method = "lm", color = "blue") 
```

### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home price using `homes_subset`.

Create 3 different permutations of this model:

(1) Price ~ City, Bedrooms, Bathrooms, SqFt, Status (lm1)
(2) Price ~ City, SqFt, Status (lm2)
(3) Try another one (lm3)

```{r}
lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)
lm2 <- lm(Price ~ City + SqFt + Status, data = homes_subset)
lm3 <- lm(Price ~ Bathrooms, data = homes_subset)

summary(lm1)
summary(lm2)
```

### Explore correlations between quantitative variables

Task: make a subset called homes_quant (starting from homes_subset) that only contains the variables from Price through SqFt.

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

homes_core <- cor(homes_quant)

corrplot(homes_core)
```

### Compare AIC values

```{r}
AIC(lm1)
AIC(lm2)
```
### Use model summary function to return multiple model outputs

```{r}
modelsummary(list(lm1,lm2,lm3))
```

### Check out diagnostic plots for lm

```{r}
plot(lm1)
```

### Use broom:augment() to return the predictions for exisiting observations

```{r}
home_predictions <- augment(lm1)
```

# Make a histogram of the residuals from this model (lm1)

```{r}
ggplot(data = home_predictions, aes(.resid)) +
  geom_histogram()
```

# BRANCHES ARE AWESOME!